Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-01 ms.tex
working on discussion despite myself2

A more readily addressable test is whether a steady-state accretion picture is capable of explaining the large scatter of typically 2-3 orders of magnitude in the observed distribution of $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at least two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).  The combination of (1) and (2) is capable of explaining much of the observed sample.

>>>>

A more readily addressable test is whether a steady-state accretion picture is capable of explaining the large scatter of typically 2-3 orders of magnitude in the observed distribution of $L_{X}/L_{\rm edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at least two effects: (1) the order of magnitude difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due to the variation in the Nuker stellar density profile $\Gamma$ at fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in combination with the significant dependence of $v_w$ on stochastic intermittency in the star formation history (Fig.~NICK).  The combination of (1) and (2) is capable of explaining much of the observed sample, especially considering that scatter in $L_{\rm X}$ due to variations in $\dot{M}$ is exacerbated by the expectation that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows.
